### 2018-06-27 README.Rmd
update readme

>>>>

## Structure

This repository is structured as follows:

* data: raw data files required by the scripts
* derived: data files produced by the scripts
* figures: figures created by the scrips
* manuscript: source files for producing the manuscript
* package: an R package with helper functions
* results: data objects outputted by the scripts
* scripts: code required to reproduce the analyses of the benchmark
